An institutional approach to attention allocation and venture resource mobilization and acquisition

### 2021-03-11 Manuscript.Rmd
kable extra is driving me crazy

```{r setup, include = FALSE}
library("papaja")
#install.packages("tinytex")
#tinytex::install_tinytex()
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

*Predictors*
**Venture attention to a resource** A common approach to measure attention allocation is to use the revealed preference of individuals to evaluate the attention structure [@gebauer2009attention]. I use the entrepreneurs’ ranked preference of the desired benefits from accelerator programs as a proxy for the attention allocation of the early-stage ventures to various resources. The GALI questionnaire asks applying entrepreneurs to rank seven acceleration benefits by perceived importance to their ventures. The seven benefits are network development (Network), e.g. with potential partners and customers, business skill development (Business Skills), mentorship from business experts (Mentorship), indirect funding through access to potential investors/funders (Access to Investors), securing direct venture funding (Direct Funding), gaining access to a group of like-minded entrepreneurs (Access to Like-minded Entrepreneurs), and awareness and credibility (Awareness and Credibility). Setting aside Awareness and Credibility and Access to Like-minded Entrepreneurs, the remaining five benefits can be categorized into three types of resources. Mentorship and Business Skills represent the development of human capital. Network help develop social capital. Direct Funding and Access to Investors improve the financial capital of early-stage ventures directly or indirectly.

@@

**Institutional level capital** To measure the level of capital of a certain resource at the country level, I used data from the World Economic Forum Global Competitiveness Index (GCI). Specificaly, I used the variable State of cluster development as a measure for institutional level social capital; Ease of finding skilled employees as a measure for institutional level human capital; and Venture capital availability, Financing of Small and Medium Enterprises, Domestic Credit Gaps as different measures of institutional level financial capital. While former measures of fiancial capital are self-explanatory, the latter variable is defined loans, purchases of non-equity securities, and trade credits and other accounts receivable provided to the private sector by financial corporations as a percentage of gross domestic products (GDP).

*Outcomes*
**Resource mobilization** is coded as a dichotomous measure *Participated* equal to one
if an applicant participate to an accelerator program of choice, and zero otherwise. I assume that pariticipating to an acceleration program is the first step to mobiliza all types of resources provided by the accelerator.

**Resource acquisition** once participants mobilize resources through participation to an accelerator, they engage in acquiring resources that garner their attention. These resources can translate into (a) raising capital from one source or many sources depending on (b) the entrepreneurs social capital (i.e. Network) or (c) hiring employees. (a), (b), and (c) are all resource acquisition outcomes.

**Performance** finaly to measure the impact on venture performance, I use the variable *Revenue* as a proxy for this outcome. This is the most commonly used performance indicator in the management in strategy litrature.

*Control Variables*
**Human Capital Index** consists of educational attainment, prior career experience in executive positions (C-level positions), team tenure, and prior founding experience [@colombo2005founders; @dimov2005human; @estrin2016human]. I measure the educational attainment of a founding team by calculating the percentage of founders with a graduate degree in the founding team (Graduate Percentage). Prior career experience in C-level executive positions (Prior C-level Executive Percentage) is measured by the percentage of founders in the founding teams holding C-level executive positions prior to the current venture. Average Team Tenure measures the average working years of the founding team members. Team Prior Founding measures the number of organizations founded by the founding team before the current venture.

@@

**Gender composition** the proportion female co-founders in each venture team.

@@

## Methods
Mixed-effects logit and probit

Given the structure of the data I used a model that incorporates both fixed- and random-effects terms. This helps me take into account the institutional (i.e. country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.

## Data analysis
I used `r cite_r("r-references.bib")` for all our analyses.
```{r message=FALSE, warning=FALSE, include=FALSE}
library(rio)
library(tidyverse)
library(janitor)
library(ggplot2)
library(psych)
library(knitr)
library(preprocessCore)

@@

with(gci, text3D(EOSQ403, EOSQ425, EOSQ109, 
  labels = gci$country,  
  col = gg.col(100), theta = 60, phi = 20,
  xlab = "Human capital", ylab = "Financail capital", zlab = "Social capital", 
  main = "Institutional level resources", cex = 0.6, 
  bty = "g", ticktype = "detailed", d = 2,
  clab = c("Urban","Pop"), adj = 1, font = 1.5))

@@

#Attention to capital - venture data

@@

@@

##Control variables

@@

```{r Human capital index}
#Graduate percentage

@@

##Gender decomposition variable

```{r Gender decomposition variable}
gali <- gali %>% drop_na(found_name1_gender)

@@

#Reverse code attention variable 
```{r message=FALSE, warning=FALSE, include=FALSE}
#Reverse code fundtion 
reverse <- function(x){x*-1 +8}

@@

#Distribution of attention

```{r fig.height=5, fig.width=8}
a <- gali %>%
  select(country, starts_with("accel_ben_rank_"))

@@

##Outcomes

#Revenues
```{r message=FALSE, warning=FALSE, include=FALSE}
gali <- gali %>% mutate(revenue_tot = gali %>%
                         select(contains("revenues")) %>% 
                         rowSums(na.rm = TRUE))
```

#Human capital acquisition 
```{r message=FALSE, warning=FALSE, include=FALSE}
gali  <- gali %>% mutate(hr_tot = gali %>%
                         select(contains("_employees")) %>% 
                         rowSums(na.rm = TRUE))
```

#Social capital acquisition 
```{r message=FALSE, warning=FALSE, include=FALSE}
gali <- gali %>% mutate(equity_sources_tot = gali %>%
                         select(contains("equityfrom")) %>% 
                         rowSums(na.rm = TRUE))
```

#Fiancial Capital acquisiton total
```{r message=FALSE, warning=FALSE, include=FALSE}
gali  <- gali %>% mutate(capital_raised0 = gali %>% select(starts_with("inv_") & ends_with("_m1")) %>% 
                         rowSums(na.rm = TRUE))

@@

#Predictor and outcome plots 
```{r}

@@

#Join all 3 datasets 
```{r message=FALSE, warning=FALSE, include=FALSE}

gali_joined <- left_join(gali, gci, by = "country")

@@

# Results

```{r message=FALSE, warning=FALSE, include=FALSE}
#Function to extract coefficients of summary table

summary_table <- function(x){ x$coefficients %>%
  as.data.frame %>%
    rename(
      "$b$" = "Estimate"
    , "SE" = "Std. Error"
    , "$t$" = "t value"
  ) %>%
  mutate(
    Effect = papaja:::prettify_terms(rownames(.))
  ) %>%
  printnum(
    digits = c(2, 2, 2, 3)
    , gt1 = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
    , zero = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
  ) %>%
  select(Effect, `$b$`, `SE`, `$t$`)}

summary_table_z <- function(x){ x$coefficients %>%
  as.data.frame %>%
    rename(
      "$b$" = "Estimate"
    , "SE" = "Std. Error"
    , "$z$" = "z value"
  ) %>%
  mutate(
    Effect = papaja:::prettify_terms(rownames(.))
  ) %>%
  printnum(
    digits = c(2, 2, 2, 3)
    , gt1 = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
    , zero = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
  ) %>%
  select(Effect, `$b$`, `SE`, `$z$`)}

@@

#Mixed model analysis - Human capital
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(lme4)
fit0hc <- glmer(participated ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country), data = gali_joined, family=binomial)

@@

hc0 <- summary_table_z(summary(fit0hc))
hc1 <- summary_table_z(summary(fit1hc))
hc00 <- summary_table(summary(fit00hc))
hc11 <- summary_table(summary(fit11hc))

rownames(hc0) <- c("Intercept","Attention to Human capital(AHC)")
rownames(hc1) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
rownames(hc00) <- c("Intercept","Attention to Human capital")
rownames(hc11) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")

kable(hc0[,-1], escape = FALSE) 
kable(hc1[,-1], escape = FALSE)
kable(hc00[,-1], escape = FALSE)
kable(hc11[,-1], escape = FALSE)

#Mixed model analysis - Financial capital
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(lme4)
fit0fc <- glmer(participated ~  accel_ben_rank_direct_funding + (accel_ben_rank_direct_funding|country), data = gali_joined, family=binomial)

summary(fit0fc)
summary(fit1fc)
summary(fit2fc)
summary(fit3fc)

fit00fc <- lmer(capital_raised_tot ~   + (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)

@@

summary(fit00fc)
summary(fit11fc)
summary(fit22fc)
summary(fit33fc)

#Mixed model analysis - Social capital

```{r echo=FALSE, message=FALSE, warning=FALSE}
fit0sc <- lmer(participated ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, REML = F)

fit1sc <- lmer(participated ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country), data = gali_joined, REML = F)

coef(summary(fit0sc))
coef(summary(fit1sc))

@@

coef(summary(fit00sc))
coef(summary(fit11sc))

@@

# Data and Methods

>>>>

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
#options(knitr.table.format = "latex")
```

```{r message=FALSE, warning=FALSE, include=FALSE}
#This is not my code. It is from https://rdrr.io/cran/gdata/src/R/cbindX.R to help me me bind cols of dfs with different number of rows

cbindX <- function(...)
{
  ## --- Setup ---

  x <- list(...)

  ## Are all objects matrices or data.frames?
  test <- sapply(x, function(z) is.matrix(z) | is.data.frame(z))
  if(any(!test)) stop("only matrices and data.frames can be used")

  ## Get maximum number of rows
  tmp <- sapply(x, nrow)
  maxi <- which.max(tmp)
  test <- tmp < tmp[maxi]

  ## --- Core ---

  ## Adding additional "empty" rows so that all objects have the same number of rows
  for(i in 1:length(tmp)) {
    if(test[i]) {
      add <- matrix(nrow=tmp[maxi] - tmp[i], ncol=ncol(x[[i]]))
      if(is.data.frame(x[[i]])) {
        add <- as.data.frame(add)
      }
      colnames(add) <- colnames(x[[i]])
      x[[i]] <- rbind(x[[i]], add)
    }
  }

  ## Column-bind all objects
  ret <- x[[1]]
  for(i in 2:length(tmp)) {
    ret <- cbind(ret, x[[i]])
  }

  ## --- Return ---
  ret
}
```

@@

**Predictors**

*Venture attention to a resource* A common approach to measure attention allocation is to use the revealed preference of individuals to evaluate the attention structure [@gebauer2009attention]. I use the entrepreneurs’ ranked preference of the desired benefits from accelerator programs as a proxy for the attention allocation of the early-stage ventures to various resources. The GALI questionnaire asks applying entrepreneurs to rank seven acceleration benefits by perceived importance to their ventures. The seven benefits are network development (Network), e.g. with potential partners and customers, business skill development (Business Skills), mentorship from business experts (Mentorship), indirect funding through access to potential investors/funders (Access to Investors), securing direct venture funding (Direct Funding), gaining access to a group of like-minded entrepreneurs (Access to Like-minded Entrepreneurs), and awareness and credibility (Awareness and Credibility). Setting aside Awareness and Credibility and Access to Like-minded Entrepreneurs, the remaining five benefits can be categorized into three types of resources. Mentorship and Business Skills represent the development of human capital. Network help develop social capital. Direct Funding and Access to Investors improve the financial capital of early-stage ventures directly or indirectly.

@@

*Institutional level capital* To measure the level of capital of a certain resource at the country level, I used data from the World Economic Forum Global Competitiveness Index (GCI). Specificaly, I used the variable State of cluster development as a measure for institutional level social capital; Ease of finding skilled employees as a measure for institutional level human capital; and Venture capital (VC) availability, Financing of Small and Medium Enterprises (SMEs), Domestic Credit Gaps as different measures of institutional level financial capital. While former measures of fiancial capital are self-explanatory, the latter variable is defined loans, purchases of non-equity securities, and trade credits and other accounts receivable provided to the private sector by financial corporations as a percentage of gross domestic products (GDP).

**Outcomes**

*Resource mobilization* is coded as a dichotomous measure *Participated* equal to one
if an applicant participate to an accelerator program of choice, and zero otherwise. I assume that pariticipating to an acceleration program is the first step to mobiliza all types of resources provided by the accelerator.

*Resource acquisition* once participants mobilize resources through participation to an accelerator, they engage in acquiring resources that garner their attention. These resources can translate into (a) raising capital from one source or many sources depending on (b) the entrepreneurs social capital (i.e. Network) or (c) hiring employees. (a), (b), and (c) are all resource acquisition outcomes.

*Performance* finaly to measure the impact on venture performance, I use the variable *Revenue* as a proxy for this outcome. This is the most commonly used performance indicator in the management in strategy litrature.

**Control Variables**

*Human Capital Index* consists of educational attainment, prior career experience in executive positions (C-level positions), team tenure, and prior founding experience [@colombo2005founders; @dimov2005human; @estrin2016human]. I measure the educational attainment of a founding team by calculating the percentage of founders with a graduate degree in the founding team (Graduate Percentage). Prior career experience in C-level executive positions (Prior C-level Executive Percentage) is measured by the percentage of founders in the founding teams holding C-level executive positions prior to the current venture. Average Team Tenure measures the average working years of the founding team members. Team Prior Founding measures the number of organizations founded by the founding team before the current venture.

@@

*Gender composition* the proportion female co-founders in each venture team.

@@

## Methods
The ventures in our sample are nested within countries. To account for such nested (or hierarchical) structure of the data, I opt for a linear mixed effects model to estimate the effects of each resource alone and when it interacts with institutional level of the resource.  This helps us account for fixed effects and random effects associated with non-nested grouping factors. Namely, it allows us to take into account the institutional (i.e. country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.

The following equation (formulas) show all the models by outcome category. Of note, I run all the following models with conrols and without controls as robustness check. Control vriables are HCI refering to Human Capital Index and GC refering to Gender composition (i.e. female percentage in a team).

**Resource mobilization**

(1)	*Participated ~  AHC + (AHC | Country)    ; AHC = Attention to Human Capital* 
(2)	*Participated ~  AHC + (AHC x Ease of finding skilled employees | Country)*
(3)	*Participated ~  AFC + (AFC | Country)   ; AHC = Attention to Financial Capital*
(4)	*Participated ~  AFC + (AFC x Financing of SMEs| Country)*   
(5)	*Participated ~  AFC + (AFC x VC availability | Country)*   
(6)	*Participated ~  AFC + (AFC x Domestic Credit Gaps | Country)*   
(7)	*Participated ~  ASC + (ASC | Country) ; ASC = Attention to Social Capital*   
(8)	*Participated ~  ASC + (ASC x State of cluster development | Country)*

**Resource acquisition**

(9) *Total employees ~ AHC + (AHC | Country)*
(10) *Total employees ~ AHC + (AHC x Ease of finding skilled employees | Country)*
(11) *Capital Raised ~ AFC + (AFC | Country)* 
(12) *Capital Raised ~ AFC + (AFC x Financing of SMEs| Country)*
(13) *Capital Raised ~ AFC + (AFC x VC availability | Country)*
(14) *Capital Raised ~ AFC + (AFC x VC availability | Country)*
(15) *Capital sources ~ ASC + (ASC | Country)*   
(16) *Capital sources ~  ASC + (ASC x State of cluster development | Country)*

**Performance**

(17)	*Revenue ~  AHC + (AHC | Country)* 
(18)	*Revenue ~  AHC + (AHC x Ease of finding skilled employees | Country)*
(19)	*Revenue ~  AFC + (AFC | Country)*
(20)	*Revenue ~  AFC + (AFC x Financing of SMEs| Country)*   
(21)	*Revenue ~  AFC + (AFC x VC availability | Country)*   
(22)	*Revenue ~  AFC + (AFC x Domestic Credit Gaps | Country)*   
(23)	*Revenue ~  ASC + (ASC | Country)*   
(24)	*Revenue ~  ASC + (ASC x State of cluster development | Country)*

## Data analysis
I used `r cite_r("r-references.bib")` for all our analyses.
```{r message=FALSE, warning=FALSE, include=FALSE}
library(rio)
library(tidyverse)
library(janitor)
library(ggplot2)
library(psych)
library(knitr)
library(preprocessCore)
library(kableExtra)

@@

with(gci, text3D(EOSQ403, EOSQ425, EOSQ109, 
  labels = gci$country,  
  col = gg.col(100), theta = 60, phi = 20,
  xlab = "Human capital", ylab = "Financial capital", zlab = "Social capital", 
  main = "Institutional level resources", cex = 0.6, 
  bty = "g", ticktype = "detailed", d = 2,
  clab = c("Urban","Pop"), adj = 1, font = 1.5))

@@

@@

## Attention to capital - venture data

@@

```{r Human capital index}
##Control variables

@@

#Graduate percentage

@@

```{r Gender decomposition variable}
##Gender composition variable

gali <- gali %>% drop_na(found_name1_gender)

@@

```{r message=FALSE, warning=FALSE, include=FALSE}
#Reverse code attention variable

#Reverse code fundtion 
reverse <- function(x){x*-1 +8}

@@

```{r fig.height=5, fig.width=8}
#Distribution of attention

a <- gali %>%
  select(country, starts_with("accel_ben_rank_"))

@@

```{r message=FALSE, warning=FALSE, include=FALSE}
#Revenues

gali <- gali %>% mutate(revenue_tot = gali %>%
                         select(contains("revenues")) %>% 
                         rowSums(na.rm = TRUE))
```

```{r message=FALSE, warning=FALSE, include=FALSE}
#Human capital acquisition

gali  <- gali %>% mutate(hr_tot = gali %>%
                         select(contains("_employees")) %>% 
                         rowSums(na.rm = TRUE))
```

```{r message=FALSE, warning=FALSE, include=FALSE}
#Social capital acquisition
gali <- gali %>% mutate(equity_sources_tot = gali %>%
                         select(contains("equityfrom")) %>% 
                         rowSums(na.rm = TRUE))
```

```{r message=FALSE, warning=FALSE, include=FALSE}
#Fiancial Capital acquisiton total
gali  <- gali %>% mutate(capital_raised0 = gali %>% select(starts_with("inv_") & ends_with("_m1")) %>% 
                         rowSums(na.rm = TRUE))

@@

```{r}
#Predictor and outcome plots

@@

```{r message=FALSE, warning=FALSE, include=FALSE}
#Join all 3 datasets 
gali_joined <- left_join(gali, gci, by = "country")
```

```{r message=FALSE, warning=FALSE}
# Results

#Function to extract coefficients of summary table

summary_table <- function(x){ x$coefficients %>%
  as.data.frame %>%
    rename(
      "$b$" = "Estimate"
    , "SE" = "Std. Error"
    , "$t$" = "t value"
    , "$p$" = "Pr(>|t|)"
  ) %>%
  mutate(
    Effect = papaja:::prettify_terms(rownames(.))
  ) %>%
  printnum(
    digits = c(2, 2, 2, 3)
    , gt1 = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
    , zero = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
  ) %>%
  select(Effect, `$b$`, `SE`, `$t$`, `$p$`)}

summary_table_z <- function(x){ x$coefficients %>%
  as.data.frame %>%
    rename(
      "$b$" = "Estimate"
    , "SE" = "Std. Error"
    , "$z$" = "z value"
    , "$p$" = "Pr(>|z|)"
  ) %>%
  mutate(
    Effect = papaja:::prettify_terms(rownames(.))
  ) %>%
  printnum(
    digits = c(2, 2, 2, 3)
    , gt1 = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
    , zero = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
  ) %>%
  select(Effect, `$b$`, `SE`, `$z$`, `$p$`)}

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Outcome: resource mobilization 
#Models
library(lme4)
fit0hc <- glmer(participated ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country), data = gali_joined, family=binomial)

fit0hc_c <- glmer(participated ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country) + HC_index + female_pct, data = gali_joined, family=binomial)

fit1hc_c <- glmer(participated ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country)+ HC_index + female_pct, data = gali_joined, family=binomial)

fit0fc <- glmer(participated ~  accel_ben_rank_direct_funding + (accel_ben_rank_direct_funding|country), data = gali_joined, family=binomial)

fit0fc_c <- glmer(participated ~  accel_ben_rank_direct_funding + (accel_ben_rank_direct_funding|country)+ HC_index + female_pct, data = gali_joined, family=binomial)

fit1fc_c <- glmer(participated ~ accel_ben_rank_direct_funding*EOSQ425 + (accel_ben_rank_direct_funding |country )+ HC_index + female_pct, data = gali_joined, family=binomial)

fit2fc_c <- glmer(participated ~ accel_ben_rank_direct_funding*EOSQ089 + (accel_ben_rank_direct_funding |country )+ HC_index + female_pct, data = gali_joined, family=binomial)

fit3fc_c <- glmer(participated ~ accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding |country)+ HC_index + female_pct, data = gali_joined, family=binomial)

fit0sc <- glmer(participated ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, family=binomial)

fit0sc_c <- glmer(participated ~ accel_ben_rank_network + (accel_ben_rank_network |country)+ HC_index + female_pct, data = gali_joined, family=binomial)

fit1sc <- glmer(participated ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country), data = gali_joined, family=binomial)

fit1sc_c <- glmer(participated ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country)+ HC_index + female_pct, data = gali_joined, family=binomial)

@@

```{r message=FALSE, warning=FALSE}
#Summary tables

hc0 <- summary_table_z(summary(fit0hc))
hc0_c <- summary_table_z(summary(fit0hc_c))
hc1 <- summary_table_z(summary(fit1hc))
hc1_c <- summary_table_z(summary(fit1hc_c))
fc0 <- summary_table_z(summary(fit0fc))
fc0_c <- summary_table_z(summary(fit0fc_c))
fc1 <- summary_table_z(summary(fit1fc))
fc1_c <- summary_table_z(summary(fit1fc_c))
fc2 <- summary_table_z(summary(fit2fc))
fc2_c <- summary_table_z(summary(fit2fc_c))
fc3 <- summary_table_z(summary(fit3fc))
fc3_c <- summary_table_z(summary(fit3fc_c))
sc0 <- summary_table_z(summary(fit0sc))
sc0_c <- summary_table_z(summary(fit0sc_c))
sc1 <- summary_table_z(summary(fit1sc))
sc1_c <- summary_table_z(summary(fit1sc_c))

rownames(hc0) <- c("Intercept","Attention to Human capital(AHC)")
rownames(hc0_c) <- c("Intercept","Attention to Human capital(AHC)", "HCI", "GC")
#rownames(hc1) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
rownames(hc1_c) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees", "HCI", "GC")
#rownames(fc0) <- c("Intercept","Attention to Financial capital")
rownames(fc0_c) <- c("Intercept","Attention to Financial capital", "HCI", "GC")
#rownames(fc1) <- c("Intercept","AFC", "Financing of SMEs", "AFCxFinancing of SMEs")
rownames(fc1_c) <- c("Intercept","AFC", "Financing of SMEs", "AFCxFinancing of SMEs", "HCI", "GC")
#rownames(fc2) <- c("Intercept","AFC", "VC Availability", "AFCxVC Availability")
rownames(fc2_c) <- c("Intercept","AFC", "VC Availability", "AFCxVC Availability", "HCI", "GC")
#rownames(fc3) <- c("Intercept","AFC", "Domestic Credit Gaps", "AFCxDomestic Credit Gaps")
rownames(fc3_c) <- c("Intercept","AFC", "Domestic Credit Gaps", "AFCxDomestic Credit Gaps", "HCI", "GC")
#rownames(sc0) <- c("Intercept","Attention to Social capital")
rownames(sc0_c) <- c("Intercept","Attention to Social capital", "HCI", "GC")
#rownames(sc1) <- c("Intercept","ASC", "State of cluster development","ASCxState of cluster development")
rownames(sc1_c) <- c("Intercept","ASC", "State of cluster development","ASCxState of cluster development", "HCI", "GC")

hc_zero <- cbindX(hc0_c[,-1], hc0[,-1]) 
hc_one <- cbindX(hc1_c[,-1], hc1[,-1]) 
fc_zero <- cbindX(fc0_c[,-1], fc0[,-1]) 
fc_one <- cbindX(fc1_c[,-1], fc1[,-1])
fc_two <- cbindX(fc2_c[,-1], fc2[,-1]) 
fc_three <- cbindX(fc3_c[,-1], fc3[,-1]) 
sc_zero <- cbindX(sc0_c[,-1], sc0[,-1]) 
sc_one <- cbindX(sc1_c[,-1], sc1[,-1])

```{r }
#Print summaries

kable(hc_zero, booktabs = T, caption = "Table 1: Effect of attention to human capital", escape = F) %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kable(hc_one, caption = "Table 2: Effect of congruency of venture attention and institutional level of human capital", format = "latex") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(fc_zero, caption = "Table 3: Effect of attention to financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(fc_one, caption = "Table 4: Effect of congruency of venture attention and institutional level (SME financing) of financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(fc_two, caption = "Table 5: Effect of congruency of venture attention and institutional level (VC) of financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(fc_three, caption = "Table 6: Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(sc_zero, caption = "Table 7: Effect of attention to social capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(sc_one, caption = "Table 8: Effect of congruency of venture attention and institutional level of social capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

#kable(sc1_c[,-1], escape = FALSE, caption = "Table 16: Effect of congruency of venture attention and institutional level of social capital - Model with controls")

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#Outcome: Resource acquistion 
library(lme4)

@@

fit00fc <- lmer(capital_raised_tot ~ + accel_ben_rank_direct_funding+ (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)

@@

@@

hc00 <- summary_table(summary(fit00hc))
hc11 <- summary_table(summary(fit11hc))
fc00 <- summary_table(summary(fit00fc))
fc11 <- summary_table(summary(fit11fc))
fc22 <- summary_table(summary(fit22fc))
fc33 <- summary_table(summary(fit33fc))
sc00 <- summary_table(summary(fit00sc))
sc11 <- summary_table(summary(fit11sc))

rownames(hc00) <- c("Intercept","Attention to Human capital")
rownames(hc11) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
rownames(fc00) <- c("Intercept","Attention to Financial capital")
rownames(fc11) <- c("Intercept","AFC", "Financing of SMEs", "AFCxFinancing of SMEs")
rownames(fc22) <- c("Intercept","AFC", "VC Availability", "AFCxVC Availability")
rownames(fc33) <- c("Intercept","AFC", "Domestic Credit Gaps", "AFCxDomestic Credit Gaps")
rownames(sc00) <- c("Intercept","Attention to Social capital")
rownames(sc11) <- c("Intercept","ASC", "State of cluster development","ASCxState of cluster development")

#kable(hc00[,-1], escape = FALSE)
#kable(hc11[,-1], escape = FALSE)
#kable(fc00[,-1], escape = FALSE)
#kable(fc11[,-1], escape = FALSE)
#kable(fc22[,-1], escape = FALSE)
#kable(fc33[,-1], escape = FALSE)
#kable(sc00[,-1], escape = FALSE)
#kable(sc11[,-1], escape = FALSE, caption = "This is the table caption")

@@
